Data Preparation

### 2019-01-18 Data Preparation.Rmd
Keeping UCM courses only

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Description)`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`,
         `Grade symbol`,
         `Booking Status (Desc.)`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         Year_numerical = `Academic Year`, # double check
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
#  mutate(as.POSIXct('2/5/2010',format='%m/%d/%Y')) %>%
  distinct
```

@@

>>>>

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Abbreviation)`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`,
         `Grade symbol`,
         `Booking Status (Desc.)`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Abbreviation)`,
         Year_numerical = `Academic Year`, # double check
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
  distinct
```

@@

### Keeping UCM program only

```{r}
d_transcript <- d_transcript %>%
  filter(`Study Program` == "7501") %>%
  select(- `Study Program`)
```
